Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an empirical study of the Moran process for the iterated Prisoner's dilemma

### 2017-10-23 main.tex
Make note of a variety of TODOs

There are three further strategies trained specifically for this study; Trained
FSM 1, 2, and 3 (TF1 - TF3). These are based on finite state machines of 16, 16,
and 8 states respectively (see Figures~\ref{fig:tf1},~\ref{fig:tf2}
and~\ref{fig:tf3}).

\begin{figure}[!hbtp]
    \centering
    \input{./tex/fsm_one.tex}
    \caption{TF1: a 16 state finite state machine with a handshake leading to
    mutual cooperation at state 4.}
    \label{fig:tf1}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \input{./tex/fsm_two.tex}
    \caption{TF2: a 16 state finite state machine with a handshake leading to
    mutual cooperation at state 16.}
    \label{fig:tf2}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \input{./tex/fsm_three.tex}
    \caption{TF3: an 8 state finite state machine.}
    \label{fig:tf3}
\end{figure}

@@

\begin{itemize}
	\item TF1 \(N=12\), 0\% noise.
	\item TF2 \(N=10\), 0\% noise.
	\item TF3 \(N=8\), 1\% noise.
\end{itemize}

Each matchup of players was run to fixation to estimate the absorption
probabilities. The trained algorithms
were run for fewer than 50 generations. Training data for this is available at
\cite{data}.

@@

Each strategy pair is run
with starting population distributions of $(1, N-1)$, $(N/2, N/2)$ and $(N-1 ,
1)$, for \(N\) from 2 through 14. The fixation probability is then empirically
computed for each combination of starting distribution and value of \(N\).  The
Axelrod library can carry out exact simulations of the Moran process. Since some
of the strategies have a high computational cost or are stochastic, samples are
taken from a large number of match outcomes for the pairs of players for use in
computing fitnesses in the Moran process. This approach was verified to agree
with unsampled calculations to a high degree of accuracy in specific cases.
This is described in Algorithms~\ref{alg:data_collection}
and~\ref{alg:moran_process}.

\begin{algorithm}[!hbtp]
        \caption{Data Collection}
        \label{alg:data_collection}
        \input{./tex/data_collection.tex}
\end{algorithm}

\begin{algorithm}[!hbtp]
        \caption{Moran process}
        \label{alg:moran_process}
        \input{./tex/moran_process_simulation.tex}
\end{algorithm}

@@

Comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
Figure~\ref{fig:comparison_deterministic}. The points represent the simulated
values and the line shows the theoretical value. Note that these are all
deterministic strategies and show a perfect match between the expected value
of (\ref{equ:fixation_probability}) and the actual Moran process for all
strategy pairs. Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
stochastic strategies. These are no longer a good match which highlights the
weakness of assuming a given interaction between two IPD strategies can be
summarised with a set of utilities as shown in
(\ref{equ:payoff_matrix}). For any given pair of strategies it is possible to
obtain \(p_{i,i-1}, p_{i,i+1}, p_{ii}\) exactly (as opposed to the
approximations offered by (\ref{equ:p_up}), (\ref{equ:p_down}) and
(\ref{equ:p_stay})). Obtaining these requires particular analysis for a given
pair and can be quite a complex endeavour for stochastic strategies with long
memory: this is not necessary for the purposes of this work.
All data generated for this validation exercise can be found
at \cite{data}.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Cooperator.pdf}
        \caption{Alternator and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Defector_v_Alternator.pdf}
        \caption{Defector and Alternator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_TfT.pdf}
        \caption{Alternator and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Cooperator_v_TfT.pdf}
        \caption{Cooperator and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Defector_v_Cooperator.pdf}
        \caption{Defector and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Defector_v_TfT.pdf}
        \caption{Defector and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/WSLS_v_TfT.pdf}
        \caption{Win Stay Lose Shift and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_WSLS.pdf}
        \caption{Alternator and Win Stay Lose Shift}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Defector_v_WSLS.pdf}
        \caption{Defector and Win Stay Lose Shift}
    \end{subfigure}%
    \caption{Comparison of theoretic and actual Moran Process fixation
             probabilities for \textbf{deterministic} strategies.}
    \label{fig:comparison_deterministic}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Random_v_Cooperator.pdf}
        \caption{Random and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Random_v_Defector.pdf}
        \caption{Random and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Random_v_TfT.pdf}
        \caption{Random and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_Cooperator.pdf}
        \caption{All C or all D and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_Defector.pdf}
        \caption{All C or all D and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Calculator_v_Random.pdf}
        \caption{Calculator and Random}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Calculator_v_ALLCorALLD.pdf}
        \caption{Calculator and All C or all D}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Calculator_v_Arrogant_QLearner.pdf}
        \caption{Calculator and Arrogant Q learner}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_TfT.pdf}
        \caption{All C or all D and Tit For Tat}
    \end{subfigure}%
    \caption{Comparison of theoretic and actual Moran Process
             fixation probabilities for \textbf{stochastic} strategies.}
    \label{fig:comparison_stochastic}
\end{figure}

@@

\begin{figure}[!hbtp]
    \begin{subfigure}{.5\textwidth}
        \centering
        \includegraphics[height=.7\textheight]{./img/boxplot_2_invade.pdf}
        \caption{The fixation probabilities for \(N=2\)}
        \label{fig:boxplot_2}
    \end{subfigure}%
    ~
    \begin{subfigure}{.5\textwidth}
        \scriptsize
        \centering
        \input{./tex/summary_top_2_invade.tex}
        \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\))}
        \label{tbl:summary_top_2}
    \end{subfigure}
    \caption{Performance of strategies for \(N=2\).}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_invade.pdf}
    \caption{\textbf{Invasion}: Ranks of all strategies according to \(x_1\) for different
    population sizes.}
    \label{fig:ranks_v_size_invade}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}{.3\textwidth}
        \centering
        \includegraphics[height=.9\textheight]{./img/boxplot_3_invade.pdf}
        \caption{\(N=3\)}
        \label{fig:boxplot_3_invade}
    \end{subfigure}%
    ~
    \begin{subfigure}{.3\textwidth}
        \centering
        \includegraphics[height=.9\textheight]{./img/boxplot_7_invade.pdf}
        \caption{\(N=7\)}
        \label{fig:boxplot_7_invade}
    \end{subfigure}%
    ~
    \begin{subfigure}{.3\textwidth}
        \centering
        \includegraphics[height=.9\textheight]{./img/boxplot_14_invade.pdf}
        \caption{\(N=14\)}
        \label{fig:boxplot_14_invade}
    \end{subfigure}
    \caption{The fixation probabilities \(x_1\).}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}{.3\textwidth}
        \centering
        \includegraphics[height=.9\textheight]{./img/boxplot_3_resist.pdf}
        \caption{\(N=3\)}
        \label{fig:boxplot_3_resist}
    \end{subfigure}%
    ~
    \begin{subfigure}{.3\textwidth}
        \centering
        \includegraphics[height=.9\textheight]{./img/boxplot_7_resist.pdf}
        \caption{\(N=7\)}
        \label{fig:boxplot_7_resist}
    \end{subfigure}%
    ~
    \begin{subfigure}{.3\textwidth}
        \centering
        \includegraphics[height=.9\textheight]{./img/boxplot_14_resist.pdf}
        \caption{\(N=14\)}
        \label{fig:boxplot_14_resist}
    \end{subfigure}
    \caption{The fixation probabilities \(x_{N-1}\).}
\end{figure}

@@

\begin{table}[!hbtp]
    \centering
    \scriptsize
    \input{./tex/change_of_rank_invade.tex}
    \caption{Invasion: Fixation ranks of some strategies according to \(x_1\) for different
    population sizes}
    \label{tbl:ranks_v_size_invade}
\end{table}

\begin{table}[!hbtp]
    \centering
    \scriptsize
    \input{./tex/change_of_rank_resist.tex}
    \caption{Resistance: Fixation ranks of some strategies according to \(x_{N-1}\) for different
    population sizes}
    \label{tbl:ranks_v_size_resist}
\end{table}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_coexist.pdf}
    \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
    population sizes.}
    \label{fig:ranks_v_size_coexist}
\end{figure}

\begin{table}[!hbtp]
    \centering
    \scriptsize
    \input{./tex/change_of_rank_coexist.tex}
    \caption{Ranks of some strategies according to \(x_{N/2}\) for different
    population sizes}
    \label{tbl:ranks_v_size_coexist}
\end{table}

@@

\begin{figure}[!htbp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{./img/correlation_heatmap_invade.pdf}
        \caption{Rank based on \(x_1\)}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{./img/correlation_heatmap_resist.pdf}
        \caption{Rank based on \(x_{N - 1}\)}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{./img/correlation_heatmap_coexist.pdf}
        \caption{Rank based on \(x_{N/2}\)}
    \end{subfigure}
    \caption{Heatmap of correlation coefficients of rankings by population size.}
    \label{fig:correlation_coefficients}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./img/cooperation_0_0_10000_TF1_array.pdf}
        \caption{TF1}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./img/cooperation_0_0_10000_TF2_array.pdf}
        \caption{TF2}
    \end{subfigure}

    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./img/cooperation_0_0_10000_TF3_array.pdf}
        \caption{TF3}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./img/cooperation_0_0_10000_CS_array.pdf}
        \caption{CS}
    \end{subfigure}
    \caption{Cooperation rate per round (over 10000 repetitions).}
    \label{fig:cooperation_rates}
\end{figure}

@@

\newpage
\bibliographystyle{plain}
\bibliography{./tex/bibliography.bib}

@@

\section{List of players}\label{app:list_of_players}

\begin{multicols}{2}
	\begin{enumerate}
		\input{./tex/list_of_players.tex}
	\end{enumerate}
\end{multicols}

>>>>

There are three further strategies trained specifically for this study; Trained
FSM 1, 2, and 3 (TF1 - TF3). These are based on finite state machines of 16, 16,
and 8 states respectively (see Figures~\ref{fig:tf1},~\ref{fig:tf2}
and~\ref{fig:tf3}).
% TODO Describe what the diagram shows

\begin{figure}[!hbtp]
    \centering
    \scalebox{.5}{\input{tex/fsm_one.tex}}
    \caption{TF1: a 16 state finite state machine with a handshake leading to
    mutual cooperation at state 4.}
    \label{fig:tf1}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \scalebox{.5}{\input{tex/fsm_two.tex}}
    \caption{TF2: a 16 state finite state machine with a handshake leading to
    mutual cooperation at state 16.}
    \label{fig:tf2}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \input{tex/fsm_three.tex}
    \caption{TF3: an 8 state finite state machine.}
    \label{fig:tf3}
\end{figure}

@@

\begin{itemize}
	\item TF1 \(N=12\), 0\% noise, 10000 repetitions per matchup
	\item TF2 \(N=10\), 0\% noise, 10000 repetitions per matchup
	\item TF3 \(N=8\), 1\% noise, 100 repetitions per matchup
\end{itemize}

Each matchup of players was run to fixation for the specified number of
repetitions to estimate the absorption probabilities. The trained algorithms
were run for fewer than 50 generations. Training data for this is available at
\cite{data}.

@@

Each strategy pair is run for 1000 repetitions of the Moran process to fixation
with starting population distributions of $(1, N-1)$, $(N/2, N/2)$ and $(N-1 ,
1)$, for \(N\) from 2 through 14. The fixation probability is then empirically
computed for each combination of starting distribution and value of \(N\).  The
Axelrod library can carry out exact simulations of the Moran process. Since some
of the strategies have a high computational cost or are stochastic, samples are
% TODO Add a bit more clarity that the cache is indeed stochastic (although not
% when using deterministic strategies.
taken from a large number of match outcomes for the pairs of players for use in
computing fitnesses in the Moran process. This approach was verified to agree
with unsampled calculations to a high degree of accuracy in specific cases.
This is described in Algorithms~\ref{alg:data_collection}
and~\ref{alg:moran_process}.
% TODO Are we clear about selection procedure?
% TODO Specify that kill off is uniformly random.

\begin{algorithm}[!hbtp]
        \caption{Data Collection}
        \label{alg:data_collection}
        \input{tex/data_collection.tex}
\end{algorithm}

\begin{algorithm}[!hbtp]
        \caption{Moran process}
        \label{alg:moran_process}
        \input{tex/moran_process_simulation.tex}
        % TODO Add description of number of turns in the IPD
\end{algorithm}

@@

Comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
Figure~\ref{fig:comparison_deterministic}. The points represent the simulated
% TODO Add description of lines shown.
values and the line shows the theoretical value. Note that these are all
deterministic strategies and show a perfect match between the expected value
of (\ref{equ:fixation_probability}) and the actual Moran process for all
strategy pairs. Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
stochastic strategies. These are no longer a good match which highlights the
weakness of assuming a given interaction between two IPD strategies can be
summarised with a set of utilities as shown in
(\ref{equ:payoff_matrix}). For any given pair of strategies it is possible to
obtain \(p_{i,i-1}, p_{i,i+1}, p_{ii}\) exactly (as opposed to the
approximations offered by (\ref{equ:p_up}), (\ref{equ:p_down}) and
(\ref{equ:p_stay})). Obtaining these requires particular analysis for a given
pair and can be quite a complex endeavour for stochastic strategies with long
memory: this is not necessary for the purposes of this work.
All data generated for this validation exercise can be found
at \cite{data}.
% TODO Include a statistical test (Bonferroni)

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{img/Alternator_v_Cooperator.pdf}
        \caption{Alternator and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{img/Defector_v_Alternator.pdf}
        \caption{Defector and Alternator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{img/Alternator_v_TfT.pdf}
        \caption{Alternator and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{img/Cooperator_v_TfT.pdf}
        \caption{Cooperator and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{img/Defector_v_Cooperator.pdf}
        \caption{Defector and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{img/Defector_v_TfT.pdf}
        \caption{Defector and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{img/WSLS_v_TfT.pdf}
        \caption{Win Stay Lose Shift and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{img/Alternator_v_WSLS.pdf}
        \caption{Alternator and Win Stay Lose Shift}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{img/Defector_v_WSLS.pdf}
        \caption{Defector and Win Stay Lose Shift}
    \end{subfigure}%
    \caption{Comparison of theoretic and actual Moran Process fixation
             probabilities for \textbf{deterministic} strategies.}
    \label{fig:comparison_deterministic}
    % TODO DEEMED Unreadable: reduce number of images.
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{img/Random_v_Cooperator.pdf}
        \caption{Random and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{img/Random_v_Defector.pdf}
        \caption{Random and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{img/Random_v_TfT.pdf}
        \caption{Random and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{img/ALLCorALLD_v_Cooperator.pdf}
        \caption{All C or all D and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{img/ALLCorALLD_v_Defector.pdf}
        \caption{All C or all D and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{img/Calculator_v_Random.pdf}
        \caption{Calculator and Random}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{img/Calculator_v_ALLCorALLD.pdf}
        \caption{Calculator and All C or all D}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{img/Calculator_v_Arrogant_QLearner.pdf}
        \caption{Calculator and Arrogant Q learner}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{img/ALLCorALLD_v_TfT.pdf}
        \caption{All C or all D and Tit For Tat}
    \end{subfigure}%
    \caption{Comparison of theoretic and actual Moran Process
             fixation probabilities for \textbf{stochastic} strategies.}
    \label{fig:comparison_stochastic}
    % TODO DEEMED Unreadable: reduce number of images.
\end{figure}

@@

\begin{figure}[!hbtp]
    \begin{subfigure}{.5\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{img/boxplot_2_invade.pdf}
        \caption{The fixation probabilities for \(N=2\)}
        \label{fig:boxplot_2}
    \end{subfigure}%
    ~
    \begin{subfigure}{.5\columnwidth}
        \scriptsize
        \centering
        \scalebox{0.95}{\input{tex/summary_top_2_invade.tex}}
        \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\))}
        % TODO Add more summary statistics to this measure
        \label{tbl:summary_top_2}
    \end{subfigure}
    \caption{Performance of strategies for \(N=2\).}
    % TODO Move the plot
    % TODO Explain this more (see comment about error bars)
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\columnwidth]{img/average_rank_vs_population_size_invade.pdf}
    \caption{\textbf{Invasion}: Ranks of all strategies according to \(x_1\) for different
    population sizes.}
    \label{fig:ranks_v_size_invade}
    % TODO Move to online appendix
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}{.3\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{img/boxplot_3_invade.pdf}
        \caption{\(N=3\)}
        \label{fig:boxplot_3_invade}
    \end{subfigure}%
    ~
    \begin{subfigure}{.3\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{img/boxplot_7_invade.pdf}
        \caption{\(N=7\)}
        \label{fig:boxplot_7_invade}
    \end{subfigure}%
    ~
    \begin{subfigure}{.3\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{img/boxplot_14_invade.pdf}
        \caption{\(N=14\)}
        \label{fig:boxplot_14_invade}
    \end{subfigure}
    \caption{The fixation probabilities \(x_1\).}
    % TODO Move to online appendix
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}{.3\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{img/boxplot_3_resist.pdf}
        \caption{\(N=3\)}
        \label{fig:boxplot_3_resist}
    \end{subfigure}%
    ~
    \begin{subfigure}{.3\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{img/boxplot_7_resist.pdf}
        \caption{\(N=7\)}
        \label{fig:boxplot_7_resist}
    \end{subfigure}%
    ~
    \begin{subfigure}{.3\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{img/boxplot_14_resist.pdf}
        \caption{\(N=14\)}
        \label{fig:boxplot_14_resist}
    \end{subfigure}
    \caption{The fixation probabilities \(x_{N-1}\).}
    % TODO Move to online appendix
\end{figure}

@@

\begin{table}[!hbtp]
    \centering
    \scriptsize
    \scalebox{0.7}{\input{tex/change_of_rank_invade.tex}}
    \caption{Invasion: Fixation ranks of some strategies according to \(x_1\) for different
    population sizes}
    \label{tbl:ranks_v_size_invade}
\end{table}

\begin{table}[!hbtp]
    \centering
    \scriptsize
    \scalebox{0.7}{\input{tex/change_of_rank_resist.tex}}
    \caption{Resistance: Fixation ranks of some strategies according to \(x_{N-1}\) for different
    population sizes}
    \label{tbl:ranks_v_size_resist}
\end{table}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\columnwidth]{img/average_rank_vs_population_size_coexist.pdf}
    \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
    population sizes.}
    \label{fig:ranks_v_size_coexist}
    % TODO Move to online appendix
\end{figure}

\begin{table}[!hbtp]
    \centering
    \scriptsize
    \input{tex/change_of_rank_coexist.tex}
    \caption{Ranks of some strategies according to \(x_{N/2}\) for different
    population sizes}
    \label{tbl:ranks_v_size_coexist}
\end{table}

@@

\begin{figure}[!htbp]
    \centering
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.9\columnwidth]{img/correlation_heatmap_invade.pdf}
        \caption{Rank based on \(x_1\)}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.9\columnwidth]{img/correlation_heatmap_resist.pdf}
        \caption{Rank based on \(x_{N - 1}\)}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.9\columnwidth]{img/correlation_heatmap_coexist.pdf}
        \caption{Rank based on \(x_{N/2}\)}
    \end{subfigure}
    \caption{Heatmap of correlation coefficients of rankings by population size.}
    % TODO Increase font
    \label{fig:correlation_coefficients}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{img/cooperation_0_0_10000_TF1_array.pdf}
        \caption{TF1}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{img/cooperation_0_0_10000_TF2_array.pdf}
        \caption{TF2}
    \end{subfigure}

    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{img/cooperation_0_0_10000_TF3_array.pdf}
        \caption{TF3}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{img/cooperation_0_0_10000_CS_array.pdf}
        \caption{CS}
    \end{subfigure}
    \caption{Cooperation rate per round (over 10000 repetitions).}
    % TODO Make less bad. Perhaps remove names altogether.
    % TODO Add better explanation of repetitions.
    \label{fig:cooperation_rates}
\end{figure}

@@

\newpage
\bibliographystyle{plain}
\bibliography{tex/bibliography.bib}
% TODO Fix repeated item.

@@

% TODO Reduce font
% TODO Add number of states for FSMs
\section{List of players}\label{app:list_of_players}

\begin{enumerate}
    \input{tex/list_of_players.tex}
\end{enumerate}
